\LARGE \bf Approximately Orchestrated Routing and Transportation Analyzer:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-15 papers/itsc_2012/final.tex
added citation to hpa

A behavior interacts with an intersection policy by sending it the agent's
desired turn, the agent's speed, the current distance from the start of the
intersection, and the length of time the agent has been idling at zero speed.
The policy replies by ordering the agent to ``stop'' or ``proceed''. The
behavior will continue to statelessly poll the policy every step until the agent
begins the turn. The policy is responsible for never changing a reply of
approval to denial when the agent could not safely honor the change. The policy
is free to allow concurrent turns in any arrangement by different agents as long
as no two simultaneous turns conflict.

\subsection{Simulation Limitations}

@@

Intersection policies are one of the most interesting aspects of the simulation
to tweak, especially in light of autonomous vehicles. Current policies include
traditional stop signs, traffic signals, and an AIM-inspired autonomous
reservation system \cite{JAIR08-dresner}. The traffic signals are further
extensible by assigning groups of non-conflicting turns at each intersection
with some duration and offset. Future policies could include signals that adapt
timings and refinements to the autonomous reservation policy.
\commentc{You can mention about using optimized traffic signal timings generated
  by commercial traffic signal optimization packages such as SYNCHRO (cite
  Husch, D. and Albeck, J. (2004) Trafficware Synchro 6 User Guide, TrafficWare,
  Albany, California.)
}

To pick turns, agent behaviors consult a route strategy. Two simple
implementations exist already: a static route using A* \cite{astar} and a
drunken walk that probabilistically moves towards the destination.  Researchers
can experiment with dynamic replanning or hierarchial planning without modifying
any code other than creating a new route implementation. Route policies could
also interact with a single central manager to gain some sort of global insight or
with autonomous intersections to avoid congestion.
\commentd{I can cite a paper for hierarchial planning. As for why, the 2
  mentioned are just examples of future work we intend to do, and I want to make
  the point that implementing both would be easy from a software engineering
  perspective.}

@@

The traffic signal policy requires timings and groups of simultaneous turns for
each intersection. The heuristic evaluated uses standard turn groups (turns from
parallel incoming directions are scheduled simultaneously, and left turns are
grouped) and employs breadth-first search to propagate timings. The goal is to
synchronize green signals so agents in some lanes do not stop for several
intersections.
\commentd{chiu recommends more details with how we propagate timings. Thoughts,
Mike?}

>>>>

A behavior interacts with an intersection policy by sending it the agent's
desired turn, the agent's speed, the current distance from the start of the
intersection, and the length of time the agent has been idling at zero speed.
The policy replies by ordering the agent to ``stop'' or ``proceed''. The
behavior will continue to statelessly poll the policy every step until the agent
begins the turn. The policy may approve an agent for entry one step and deny it
the next, so long as the agent could safely brake without danger of entering the
intersection. The policy is free to allow concurrent turns in any arrangement
by different agents as long as no two simultaneous turns conflict.

\subsection{Current Limitations}

@@

Intersection policies are one of the most interesting aspects of the simulation
to tweak, especially in light of autonomous vehicles. Current policies include
traditional stop signs, traffic signals, and an AIM-inspired autonomous
reservation system \cite{JAIR08-dresner}. The traffic signals are further
extensible by assigning groups of non-conflicting turns at each intersection
with some duration and offset. Future policies could include signals that adapt
timings and refinements to the autonomous reservation policy.

To pick turns, agent behaviors consult a route strategy. Two simple
implementations exist already: a static route using A* \cite{astar} and a
drunken walk that probabilistically moves towards the destination. Researchers
can experiment with dynamic replanning or hierarchial planning
\cite{Botea04nearoptima} without modifying any code other than creating a new
route implementation. Route policies could also interact with a single central
manager to gain some sort of global insight or with autonomous intersections to
avoid congestion.

@@

The traffic signal policy requires timings and groups of simultaneous turns for
each intersection. The heuristic evaluated uses standard turn groups (turns from
parallel incoming directions are scheduled simultaneously, and left turns are
grouped) and employs breadth-first search to propagate timings. The goal is to
synchronize green signals so agents in some lanes do not stop for several
intersections.
\commentd{chiu recommends more details with how we propagate timings. Thoughts,
Mike?}
\commentc{You can mention about using optimized traffic signal timings generated
  by commercial traffic signal optimization packages such as SYNCHRO (cite
  Husch, D. and Albeck, J. (2004) Trafficware Synchro 6 User Guide, TrafficWare,
  Albany, California.)
}
